---
title: "Getting Started: Diamonds"
author: "L Little"
date: 2020-07-10
output:
  github_document:
    toc: true
---

*Purpose*: Throughout this course, you'll complete a large number of *exercises* and *challenges*. Exercises are meant to introduce content with easy-to-solve problems, while challenges are meant to make you think more deeply about and apply the content. The challenges will start out highly-scaffolded, and become progressively open-ended.

In this challenge, you will go through the process of exploring, documenting, and sharing an analysis of a dataset. We will use these skills again and again in each challenge.

<!-- include-rubric -->
# Grading Rubric
<!-- -------------------------------------------------- -->

Unlike exercises, **challenges will be graded**. The following rubrics define how you will be graded, both on an individual and team basis.

## Individual
<!-- ------------------------- -->

| Category | Unsatisfactory | Satisfactory |
|----------|----------------|--------------|
| Effort | Some task __q__'s left unattempted | All task __q__'s attempted |
| Observed | Did not document observations | Documented observations based on analysis |
| Supported | Some observations not supported by analysis | All observations supported by analysis (table, graph, etc.) |
| Code Styled | Violations of the [style guide](https://style.tidyverse.org/) hinder readability | Code sufficiently close to the [style guide](https://style.tidyverse.org/) |

## Team
<!-- ------------------------- -->

| Category | Unsatisfactory | Satisfactory |
|----------|----------------|--------------|
| Documented | No team contributions to Wiki | Team contributed to Wiki |
| Referenced | No team references in Wiki | At least one reference in Wiki to member report(s) |
| Relevant | References unrelated to assertion, or difficult to find related analysis based on reference text | Reference text clearly points to relevant analysis |

## Due Date
<!-- ------------------------- -->

All the deliverables stated in the rubrics above are due on the day of the class discussion of that exercise. See the [Syllabus](https://docs.google.com/document/d/1jJTh2DH8nVJd2eyMMoyNGroReo0BKcJrz1eONi3rPSc/edit?usp=sharing) for more information.

```{r setup}
library(tidyverse)
```

# Data Exploration
<!-- -------------------------------------------------- -->

In this first stage, you will explore the `diamonds` dataset and document your observations.

__q1__ Create a plot of `price` vs `carat` of the `diamonds` dataset below. Document your observations from the visual.

*Hint*: We learned how to do this in `e-vis00-basics`!

```{r q1-task}
## TASK: Plot `price` vs `carat` below
## Your code here!

ggplot(data= diamonds) + geom_smooth(mapping = aes(y = price, x = carat))
```

**Observations**:
This plot shows that up to ~2.5 carats, higher carat correlates with higher 
price. Beyond 2.5 carats the correlation generally still applies, but there is 
a 'valley' in between 2.5 and 3.5 carats. I will further examine a histogram
to see if if data is sparse beyond 2.5 carats as I suspect.

```{r}
ggplot(data = diamonds, aes(carat)) + geom_histogram(binwidth = 0.02)
```

```{r}
ggplot(data = diamonds, aes(carat)) + geom_histogram(binwidth = 0.3)
```

***Observations***
These two histograms provide very different information.
- smaller binning shows that some sizes are much more common than others
- larger binning show that smaller diamonds are much more common than larger
diamonds. This makes sense as diamonds are often used in rings and very large
rings are undesirable

__q2__ Create a visualization showing variables `carat`, `price`, and `cut` 
simultaneously. Experiment with which variable you assign to which aesthetic 
(`x`, `y`, etc.) to find an effective visual.

```{r q2-task}
## TASK: Plot `price`, `carat`, and `cut` below
## Your code here!
ggplot(data=diamonds) + 
  geom_smooth(mapping = aes(x = carat, y = price, color = cut))
```

**Observations**:

- Seems like the strange price dip is because there are not high quality 
diamonds that exist at large carats. 
- Generally, at a given carat, higher quality diamonds are more expensive.

__Further plots__

I was also interested in seeing what the average carat was for each size of 
diamond.
```{r}
ggplot(data=filter(diamonds)) + geom_boxplot(mapping = aes(x = cut, y = carat),
                                             outlier.shape = NA)
```

Generally, the higher the quality, the smaller the average diamond of that 
quality. 

I was also curious how many of each diamond type there were.
```{r}
ggplot(data = diamonds, aes(cut)) + 
  geom_bar() +
  scale_fill_brewer(palette= "Dark2")
```

It seems that there are many more high quality diamonds than low quality 
diamonds.
