---
title: "RMS Titanic"
author: "L Little"
date: 2020-07
output:
  github_document:
    toc: true
---

*Purpose*: Most datasets have at least a few variables. Part of our task in analyzing a dataset is to understand trends as they vary across these different variables. Unless we're careful and thorough, we can easily miss these patterns. In this challenge you'll analyze a dataset with a small number of categorical variables and try to find differences among the groups.

*Reading*: (Optional) [Wikipedia article](https://en.wikipedia.org/wiki/RMS_Titanic) on the RMS Titanic.

<!-- include-rubric -->
# Grading Rubric
<!-- -------------------------------------------------- -->

Unlike exercises, **challenges will be graded**. The following rubrics define how you will be graded, both on an individual and team basis.

## Individual
<!-- ------------------------- -->

| Category | Unsatisfactory | Satisfactory |
|----------|----------------|--------------|
| Effort | Some task __q__'s left unattempted | All task __q__'s attempted |
| Observed | Did not document observations | Documented observations based on analysis |
| Supported | Some observations not supported by analysis | All observations supported by analysis (table, graph, etc.) |
| Code Styled | Violations of the [style guide](https://style.tidyverse.org/) hinder readability | Code sufficiently close to the [style guide](https://style.tidyverse.org/) |

## Team
<!-- ------------------------- -->

| Category | Unsatisfactory | Satisfactory |
|----------|----------------|--------------|
| Documented | No team contributions to Wiki | Team contributed to Wiki |
| Referenced | No team references in Wiki | At least one reference in Wiki to member report(s) |
| Relevant | References unrelated to assertion, or difficult to find related analysis based on reference text | Reference text clearly points to relevant analysis |

## Due Date
<!-- ------------------------- -->

All the deliverables stated in the rubrics above are due on the day of the class discussion of that exercise. See the [Syllabus](https://docs.google.com/document/d/1jJTh2DH8nVJd2eyMMoyNGroReo0BKcJrz1eONi3rPSc/edit?usp=sharing) for more information.

```{r setup}
library(tidyverse)

df_titanic <- as_tibble(Titanic)
```

*Background*: The RMS Titanic sank on its maiden voyage in 1912; about 67% of its passengers died.

# First Look
<!-- -------------------------------------------------- -->

__q1__ Perform a glimpse of `df_titanic`. What variables are in this dataset?

```{r q1-task}
## TASK: Perform a `glimpse` of df_titanic
glimpse(df_titanic)
```

**Observations**:

Variables are:

- Class
- Sex
- Age
- survived
- number (n)

__q2__ Skim the [Wikipedia article](https://en.wikipedia.org/wiki/RMS_Titanic) on the RMS Titanic, and look for a total count of passengers. Compare against the total computed below. Are there any differences? Are those differences large or small? What might account for those differences?

```{r q2-summary}
## NOTE: No need to edit! We'll cover how to
## do this calculation in a later exercise.
df_titanic %>% summarize(total = sum(n))
```

**Observations**:

- According to wikipeda, there were 3327 total people, so this database seems to 
be missing ~1000 passengers, almost 1/3 of the total. 
- Perhaps this data was collected differently - for example passenger manifest 
instead of sold tickets. 

__q3__ Create a plot showing the count of passengers who *did* survive, along with aesthetics for `Class` and `Sex`. Document your observations below.

*Note*: There are many ways to do this.

```{r q3-task}
## TASK: Visualize counts against `Class` and `Sex`
df_titanic %>%
  filter(Survived == 'Yes' & Age == 'Adult') %>%
  ggplot() +
  geom_col(aes(x = Class, y = n, fill = Sex), position = 'dodge') + 
  scale_fill_brewer(palette= "Accent")
```

**Observations**:

I will only consider Adults here, to be consistent with 
q4 (explained in q4)

- Out of everyone who survived, most of them were either Crew or 1st class
- Many more 1st and 2nd class women survived than 1st and 2nd class men
- Many more male crew survived then female crew
- An equal number of 3rd class men and women survived.

# Deeper Look
<!-- -------------------------------------------------- -->

Raw counts give us a sense of totals, but they are not as useful for understanding differences between groups. This is because the differences we see in counts could be due to either the relative size of the group OR differences in outcomes for those groups. To make comparisons between groups, we should also consider *proportions*.[1]

The following code computes proportions within each `Class, Sex, Age` group.

```{r compute-prop}
## NOTE: No need to edit! We'll cover how to
## do this calculation in a later exercise.
df_prop <-
  df_titanic %>%
  group_by(Class, Sex, Age) %>%
  mutate(
    Total = sum(n),
    Prop = n / Total
  ) %>%
  ungroup()
df_prop
```

__q4__ Replicate your visual from q3, but display `Prop` in place of `n`. Document your observations, and note any new/different observations you make in comparison with q3.

```{r q4-task}
df_prop %>%
  filter(Survived == 'Yes') %>%
  ggplot() +
  geom_col(aes(x = Class, y = Prop, fill = Sex), position = 'stack') + 
  scale_fill_brewer(palette= "Accent")

```

**Observations**:

- This graph doesn't make any sense unless I ALSO facet/filter by age or make a new 
group_by() proportion that doesn't consider age. The geom_col() function 
is just adding together proportions in a nonsensical way since there are 
multiple proportion values for each Sex and Class group (it is adding 
the proprtion of Children and Adults who survived in each Age and Class). 
Therefore for this quesiton I will only consider
adults. 
- Related note - while it makes sense to use a 'stack' visualization for 
a total count, it generally does not make sense to use for proportions since 
you cannot just add proportions together in the same way.

- It is also weird that when I change the code to position = 'dodge' instead 
it seems like the bars cut off at 1 for no reason? Why is that? (shown below)

```{r q4-weird-Graph}
df_prop %>%
  filter(Survived == 'Yes') %>%
  ggplot() +
  geom_col(aes(x = Class, y = Prop, fill = Sex), position = 'dodge')  + 
  scale_fill_brewer(palette= "Accent")
```

Ok now for the graph with only 'Adult's considered
```{r q4-task-pt2}
df_prop %>%
  filter(Survived == 'Yes' & Age == 'Adult') %>%
  ggplot() +
  geom_col(aes(x = Class, y = Prop, fill = Sex), position = 'dodge')  + 
  scale_fill_brewer(palette= "Accent")
```
**Observations**

- Even though many fewer female crew survived total, female crew members survived
at a much higher proportion than male crew members.
- Overall, women of any given class were twice as likely to survive as men of 
the same class. 
- The group where any given member was most likely to survive was 1st class women
- The group where any given member was least likely to survive was 2nd class men
- For women, higher class led to being more likely to survive. Not so with men.
- Fewer than 1/3 of the total men survived. 
__q5__ Create a plot showing the group-proportion of passengers who *did* survive, along with aesthetics for `Class`, `Sex`, *and* `Age`. Document your observations below.

*Hint*: Don't forget that you can use `facet_grid` to help consider additional variables!

```{r q5-task}
df_prop %>%
  filter(Survived == 'Yes') %>%
  ggplot() +
  geom_col(aes(x = Class, y = Prop, fill = Sex), position = 'dodge') +
  facet_grid("Age") + 
  scale_fill_brewer(palette= "Accent")
```

**Observations**:

- Children in general were much more likely to survive
- All of the 1st and 2nd class children survived. 
- 3rd class children survived in about the same proportion as 3rd class adults 
- There were no childern on the crew (not surprising).

# Notes
<!-- -------------------------------------------------- -->

[1] This is basically the same idea as [Dimensional Analysis](https://en.wikipedia.org/wiki/Dimensional_analysis); computing proportions is akin to non-dimensionalizing a quantity.
