---
title: "Project"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```

First import the first level of the dataset with the correct column names.
```{r Level1, include = FALSE}
string <-"Nss69/Nss69_1.2/Data/R6912L01.TXT"
imported_data_lvl1 <- read_tsv(file = string, col_names = FALSE)


lvl1 <- imported_data_lvl1 %>%
   separate(col = 'X1', into = c('Centre, Round',
                                 'RowID',
                                 'Level',
                                 'Filler',
                                 'Informants relation to head',
                                 'Response Code',
                                 'Survey Code',
                                 'Reason for substitution',
                                 'Sp. Characters for OK stamp',
                                 'Blank',
                                 'SSC',
                                 'NSS',
                                 'NSC',
                                 'MLT'
                                 ),
            sep=c(3,
                  34,
                  36,
                  41,
                  42,
                  43,
                  44,
                  45,
                  47,
                  126,
                  127,
                  130,
                  133,
                  143)) %>%
   separate(col = 'RowID', into = c('FSU Serial number',
                                    'Round',
                                    'Schedule Number',
                                    'Sample',
                                    'Sector',
                                    'State',
                                    'Region',
                                    'District',
                                    'Stratum',
                                    'Sub-Stratum',
                                    'Sub-Round',
                                    'Sub-Sample',
                                    'FOD Sub-Region',
                                    'hg/ sb Number',
                                    'Second Stage Stratum no.',
                                    'Sample household no.'),
            sep = c(5,
                    7,
                    10,
                    11,
                    12,
                    14,
                    15,
                    17,
                    19,
                    21,
                    22,
                    23,
                    27,
                    28,
                    29
                    ),
            remove = FALSE
   )

```
Next import the 'Level 2' of the dataset. The first 34 bytes should match up with 
the level 1 dataset. 
```{r Level2, include = FALSE}
string <-"Nss69/Nss69_1.2/Data/R6912L02.TXT"
imported_data_lvl2 <- read_tsv(file = string, col_names = FALSE)


lvl2 <- imported_data_lvl2 %>%
   separate(col = 'X1', into = c('Centre, Round',
                                 'RowID',
                                 'Level',
                                 'Filler',
                                 'Household size-Male',
                                 'Household size-Female',
                                 'Household size- Total',
                                 'Gender of the head',
                                 'Age of head',
                                 'Highest level of education among male',
                                 'Highest level of education among female',
                                 'Principal industry(NIC-2008)',
                                 'Principal occupation(NCO-2004)',
                                 'Household type',
                                 'Religion' ,
                                 'Social group',
                                 'Land possessed',
                                 'Tenurial status of dwelling',
                                 'Area type where dwelling unit located',
                                 'Maximum distance to the place of work of the earner member',
                                 'Special characters for OK stamp',
                                 'Blank',
                                 'SSC',
                                 'NSS',
                                 'NSC',
                                 'MLT'
                                 ),
            sep = c(3,
                    34,
                    36,
                    41,
                    43,
                    45,
                    47,
                    48,
                    49,
                    51,
                    53,
                    58,
                    61,
                    62,
                    63,
                    64,
                    66,
                    67,
                    68,
                    69,
                    71,
                    126,
                    127,
                    130,
                    133,
                    143)) 
```
And then we import level 3

```{r Level3, include = FALSE}
string <-"Nss69/Nss69_1.2/Data/R6912L03.TXT"
imported_data_lvl3 <- read_tsv(file = string, col_names = FALSE)


lvl3 <- imported_data_lvl3 %>%
   separate(col = 'X1', into = c('Centre, Round',
                                 'RowID',
                                 'Level',
                                 'Filler',
                                 'Purchase(Rs)',
                                 'Home produced stock (Rs.)',
                                 'Exchange of goods & services (Rs.)',
                                 'Gifts & loans (Rs.)',
                                 'Free collection (Rs.)',
                                 'Total (items 17 to 21) (Rs.)',
                                 'Whether amount spent on construction/ first-hand purchase of houses/flats for residential purpose',
                                 'Amount spent during last 365 days (Rs.)',
                                 'Sources of finance 1',
                                 'Sources of finance 2',
                                 'Sources of finance 3' ,
                                 'Sources of finance 4',
                                 'Special characters for OK stamp',
                                 'Blank',
                                 'SSC',
                                 'NSS',
                                 'NSC',
                                 'MLT'
                                 ),
            sep = c(3,
                    34,
                    36,
                    41,
                    49,
                    57,
                    65,
                    73,
                    81,
                    89,
                    90,
                    98,
                    100,
                    102,
                    104,
                    106,
                    108,
                    126,
                    127,
                    130,
                    133,
                    143)) 
```

Next import the population dataset (from a different source). We hope to align this
with the first two datasets, but need to check how to do that. I did manually
remove all of the * characters from the District Codes 69 file.
```{r PopData, include = FALSE}
df_3 <- read_csv('A-1_NO_OF_VILLAGES_TOWNS_HOUSEHOLDS_POPULATION_AND_AREA.csv', col_names = TRUE,
         skip = 4)
df_4 <- read_csv('Nss69/Nss69_1.2/Supporting Documents_69_1.2/District Codes_69.csv',
                 col_names = TRUE, skip = 2)
df_4_mod <-
   df_4 %>%
   mutate('Name' = str_extract(`District Name`, pattern = "([^\\*\\()]+)") %>%
   str_trim())

df_3_mod <- df_3 %>%
   filter(`India/ State/ Union Territory/ District/ Sub-district` == 'DISTRICT') %>%
   mutate('District Name' = Name)

df_pop <-
  left_join(
    df_3_mod,
    df_4_mod,
    by = c("Name" = "District Name")
  ) %>%
   filter(`Total/ Rural/ Urban` %in% c('Rural', 'Urban'))

df_pop <- df_pop %>% 
   mutate(rural_urban = if_else(pull(df_pop, `Total/ Rural/ Urban`) == 'Rural', 1, 2)) %>%
   unite(c(st,dc,rural_urban), col = 'state_district_sector', remove = FALSE)

```
Now we have a population dataset!


Lets check that the multiplier values are the same for both tabels
```{r Tidying}
check1 <- lvl1 %>%
   count(`MLT`, sort = TRUE)

check2 <- lvl2 %>%
   count(`MLT`, sort = TRUE)

all_equal(check1, check2)
```
Seems ok! 
Lets combine the two levels into one dataframe


```{r Concat, results = 'hide'}

df_joined <- full_join(lvl1, lvl2, by = 'RowID', keep = FALSE)
df_joined <- full_join(df_joined, lvl3, by = 'RowID', keep = FALSE)

df_joined <- df_joined %>%
   unite(c(State, District, Sector), col = 'state_district_sector', remove = FALSE)

df_all <- left_join(df_joined, df_pop, by = 'state_district_sector', keep = FALSE)


```
 Lets covert the land column from an input code to a real numerical value.
 The input is in ranges, so we are taking the average of the range to repesent 
 that value. This is because we want to be able to treat land area as a numeric 
 variable. Note that the last range is 'greater that 8.01 hectares', which we
 will represent numerically as 10 hectares. This will mess up any non-robust 
 measurements such as a mean, since the real value may be much more than 10. 
 
```{r Convert Land Columns}

df_1 <- df_all %>%
   filter(`Land possessed` == '01') %>%
   mutate(land_area = 0.0025)

df_2 <- df_all %>%
   filter(`Land possessed` == '02') %>%
   mutate(land_area = 0.0125)

df_3 <- df_all %>%
   filter(`Land possessed` == '03') %>%
   mutate(land_area = 0.115)

df_4 <- df_all %>%
   filter(`Land possessed` == '04') %>%
   mutate(land_area = 0.31)

df_5 <- df_all %>%
   filter(`Land possessed` == '05') %>%
   mutate(land_area = 0.71)

df_6 <- df_all %>%
   filter(`Land possessed` == '06') %>%
   mutate(land_area = 1.505)

df_7 <- df_all %>%
   filter(`Land possessed` == '07') %>%
   mutate(land_area = 2.505)

df_8 <- df_all %>%
   filter(`Land possessed` == '08') %>%
   mutate(land_area = 3.505)

df_10 <- df_all %>%
   filter(`Land possessed` == '10') %>%
   mutate(land_area = 5.01)

df_11 <- df_all %>%
   filter(`Land possessed` == '11') %>%
   mutate(land_area = 7.01)

df_12 <- df_all %>%
   filter(`Land possessed` == '12') %>%
   mutate(land_area = 10)

df_all <- bind_rows(df_1, df_2, df_3, df_4, df_5, df_6, df_7, df_8, df_10, df_11, df_12)
```


```{r Select}

#Pair down the frame to something more manageable
df_all_selected_mlt <-
  df_all %>%
  select(
    `RowID`,
    `state_district_sector`,
    `MLT`,
    `land_area`,
    `Land possessed`,
    `Household Expenditure` = `Total (items 17 to 21) (Rs.)`,
    `Sources of finance 1`,
    `Sources of finance 2`,
    `Sources of finance 3`,
    `Sources of finance 4`,
    `Name`,
    `Rural_Urban` = `Total/ Rural/ Urban`,
    `Number of households`,
    `Population` = `Population Persons`,
    `Area` = `Area  (In sq. km)`,
    `Population per sq. km.`,
    `District Name`,
    `State Name`
  ) %>%
   mutate(MLT = as.numeric(MLT)) %>%
   mutate(`Household Expenditure` = as.numeric(`Household Expenditure`))

df_all_selected <-
   df_all_selected_mlt %>% 
      group_by(RowID) %>% 
      slice(rep(1:n(), each = ceiling(`MLT`/100000)))

```

 ## Areas to Explore
 
 'results' are 
 - land  Schedule 1.2 item 13 block 3
 - spending amount (item 22, block 3)
 
 'indicators' are
 - population density
       - we found a separate dataset for population density of rural vs urban 
      areas for each district
      - The rural vs urban distinction appears on item 5 block 1 of the schedule
      - we will compile those two and assume that the definition of urban and rural
      is close enough
 - primary income source (item 10, block 3)
 
 - we want to filter to only look at certain population densities to 10k-16k people / km^2

```{r}
df_all_selected %>% 
   filter(Rural_Urban != 'NA') %>%
   ggplot() +
   geom_point(
      mapping = aes(
         x = `Population per sq. km.`,
         y = `land_area`,
         color = `Rural_Urban`)
      ) +
   geom_smooth(
      mapping = aes(
         x = `Population per sq. km.`,
         y = `land_area`
         )
      ) +
   # geom_vline(aes(xintercept = 287)) +
   # geom_vline(aes(xintercept = 9751)) +
   # geom_vline(aes(xintercept = 13233)) +
   scale_y_log10() +
   labs(
    y= "Land Possessed (Ha)",
    color = "Rural vs. Urban"
   )
   #coord_fixed(ratio=10000)

   #facet_grid(. ~ Rural_Urban)

```
```{r}

#Household expenditure
df_all_selected %>%
   #filter(`Household Expenditure` < 1000000) %>% 
   filter(Rural_Urban != 'NA') %>%
   ggplot() +
   geom_point(
      mapping = aes(
         x = `Population per sq. km.`,
         y = `Household Expenditure`,
         color = `Rural_Urban`)
      ) +
   geom_smooth(
      mapping = aes(
         x = `Population per sq. km.`,
         y = `Household Expenditure`
         )
      ) +
   geom_vline(aes(xintercept = 287)) +
   geom_vline(aes(xintercept = 9751)) +
   geom_vline(aes(xintercept = 13233)) +
   scale_y_log10() +
   labs(
    y= "Household Expenditure (Rupees/Month)",
    color = "Rural vs. Urban"
  )
```


```{r}
df_all_selected_mlt %>%
   group_by(`Sources of finance 1`, Rural_Urban) %>%
   filter(Rural_Urban=='Rural' | Rural_Urban == 'Urban')%>%
   filter(`Sources of finance 1` == '01' |
          `Sources of finance 1` == '02'|
          `Sources of finance 1` == '03'|
          `Sources of finance 1` == '04'|
          `Sources of finance 1` == '05'|
          `Sources of finance 1` == '06'|
          `Sources of finance 1` == '07'|
          `Sources of finance 1` == '08'|
          `Sources of finance 1` == '09'|
          `Sources of finance 1` == '10'
          ) %>%
   summarize(num = sum(MLT))%>%
   ggplot() + 
   geom_col(mapping = aes(x = `Sources of finance 1`, y = num, fill = Rural_Urban)) +
   facet_grid(Rural_Urban ~ .)
```
This is strange and somewhat alarming because urban areas should have only had the number options of 
1,2,3, and 9. But herew we see that some number of people in urban areas are listed as having options 5, 7, 8, and 10 
marked off. 
```{r}
df_all_selected %>% 
   filter(Rural_Urban != 'NA') %>%
   filter(`Household Expenditure` < 30000) %>%
   ggplot() +
   geom_smooth(mapping = aes(y = `land_area`, x = `Household Expenditure`, color = Rural_Urban)) +
   geom_point(mapping = aes(y = `land_area`, x = `Household Expenditure`, color = Rural_Urban)) +
   geom_point(data = filter(df_all_selected, `Rural_Urban` != 'NA' & `Household Expenditure` > 30000 & `Household Expenditure` < 1000000),
              mapping = aes(y = `land_area`, x = `Household Expenditure`, color = Rural_Urban)) + 
   scale_y_continuous(breaks=c(0.01,0.3, 0.71,1.5, 2.5,3.5,5, 7,10)) +
   labs( x = "Household Expenditure (Rupees)", y = "Land Possession (hectares)")
```
This graph is no good because it uses a mean-type function which as described above
does not work for this data since the upper values of `10` could be much higher.

Instead a median-type graph should be used.

```{r}
df_all_selected %>% 
   filter(Rural_Urban != 'NA') %>%
   filter(`Household Expenditure` < 50000) %>%
   mutate(bin = factor(`Household Expenditure`%/%5000*5000)) %>%
   ggplot(mapping = aes(x = bin, y = `land_area`)) +
   geom_boxplot() +
   #geom_smooth(mapping = aes(y = `land_area`, x = `Household Expenditure`, color = Rural_Urban)) +
   #geom_point(mapping = aes(y = `land_area`, x = `Household Expenditure`, color = Rural_Urban)) +
   #geom_point(data = filter(df_all_selected, `Rural_Urban` != 'NA' & `Household Expenditure` > 50000 & `Household Expenditure` < 1000000),
   #           mapping = aes(y = `land_area`, x = `Household Expenditure`, color = Rural_Urban)) + 
   scale_y_continuous(breaks=c(0.01,0.3, 0.71,1.5, 2.5,3.5,5, 7,10), limits = c(0,0.5)) +
   facet_wrap( ~ Rural_Urban)
   #labs( x = "Household Expenditure (Rupees)", y = "Land Possession (hectares)")
```
Unfortunately it is hard to tell much from this graph.

```{r}
df_bin <- df_all_selected %>% 
   filter(`Household Expenditure` < 25000 & `Rural_Urban` != 'NA') %>%
   mutate(bin = `Household Expenditure`%/%5000*5000)
df_bin %>%
   ggplot() +
   geom_histogram(mapping = aes(x = `land_area`), breaks = c(0.0025,0.0125,0.115,0.31, 0.71,1.505, 2.505,3.505,5.01,7.01,10)) +
#   scale_x_log10()+
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 
   labs(x = "Land Possession (hectares)")

df_bin <- df_all_selected %>% 
   filter(`Household Expenditure` < 25000 & `Rural_Urban` != 'NA') %>%
   mutate(bin = `Household Expenditure`%/%5000*5000)
df_bin %>%
   ggplot() +
   geom_histogram(mapping = aes(x = `land_area`), breaks = c(0.0025,0.0125,0.115,0.31, 0.71,1.505, 2.505,3.505,5.01,7.01,10)) +
   scale_x_log10()+
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
   labs(x = "Land Possession (hectares)")
```

This is a veeery long distribution (and it in already artificially shortened) What would it look like if we put it on a log scale?


```{r}
df_bin <- df_all_selected %>% 
   filter(`Household Expenditure` < 20000 & `Rural_Urban` != 'NA') %>%
   mutate(bin = `Household Expenditure`%/%5000*5000)
df_bin %>%
   ggplot() +
   geom_histogram(mapping = aes(x = `land_area`), breaks = c(0.0025,0.0125,0.115,0.31, 0.71,1.505, 2.505,3.505,5.01,7.01,10)) +
   scale_x_log10()+
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
   facet_grid(.~ bin, labeller= labeller(bin = c('0' ="0-5k", '5000' ="5-10k", '10000'="10-15k", '15000'="15-20k")))+
      labs(x = "Land Possession (hectares)")


df_bin
```
```{r}
df_bin <- df_all_selected %>% 
   filter(`Household Expenditure` < 20000 & `Rural_Urban` != 'NA') %>%
   mutate(bin = `Household Expenditure`%/%5000*5000)
df_bin %>%
   ggplot() +
   geom_histogram(mapping = aes(x = `land_area`, fill = Rural_Urban), breaks = c(0.0025,0.0125,0.115,0.31, 0.71,1.505, 2.505,3.505,5.01,7.01,10)) +
   scale_x_log10()+
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
   facet_grid(Rural_Urban~ bin, labeller= labeller(bin = c('0' ="0-5k", '5000' ="5-10k", '10000'="10-15k", '15000'="15-20k")))+
      labs(x = "Land Possession (hectares)")


df_bin
```
How much of the population are we capturing with our cutoff?
```{r}
df_all_selected %>%
   summarize(n = n())

df_all_selected %>%
   filter(`Household Expenditure` < 20000) %>%
   summarize(n=n())
```

```{r}
df_all_selected %>% 
   filter(Rural_Urban != 'NA') %>%
   filter(`Household Expenditure` < 1000000) %>%
   ggplot() +
   geom_histogram(mapping = aes(x = `Household Expenditure`, fill = Rural_Urban), binwidth = 5000) +
   scale_x_continuous(breaks=c(0,10000,20000,30000,40000,50000,100000))+
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
   facet_grid(Rural_Urban ~.)+ 
   labs( x = "Household Expenditure (Rupees)")


#do this numerically
df_all_selected %>%
   group_by(Rural_Urban) %>%
   filter(Rural_Urban=='Rural' | Rural_Urban == 'Urban')%>%
   summarize(num = n())

df_all_selected %>%
   filter(`Household Expenditure` < 20000) %>%
   group_by(Rural_Urban) %>%
   filter(Rural_Urban=='Rural' | Rural_Urban == 'Urban')%>%
   summarize(num = n()/c(15427,5012))
```
```{r}
df_all_selected %>% 
   filter(Rural_Urban != 'NA') %>%
   ggplot() +
   geom_histogram(mapping = aes(x = `Population per sq. km.`, fill = Rural_Urban)) +
   facet_grid(Rural_Urban ~.)
   labs( x = "Household Expenditure (Rupees)")
```

```{r}
df_land <- df_all_selected_mlt %>%
   group_by(`land_area`, `Rural_Urban`) %>%
   filter(Rural_Urban != 'NA') %>%
   summarise(sum = sum(`MLT`)) 

df_land %>% 
   ggplot() + 
   geom_col(mapping = aes(x = `land_area`, y = sum, fill = Rural_Urban), position = 'dodge') 
   
df_land %>% 
   ggplot() + 
   geom_col(mapping = aes(x = `land_area`, y = sum, fill = Rural_Urban), position = 'dodge') + 
   scale_x_log10()
```
```{r}
df_land <- df_all_selected_mlt %>%
   group_by(`Land possessed`, `Rural_Urban`) %>%
   filter(Rural_Urban != 'NA') %>%
   summarise(sum = sum(`MLT`))

df_land %>% 
   ggplot() + 
   geom_col(mapping = aes(x = `Land possessed`, y = sum, fill = Rural_Urban), position = 'dodge')
```
```{r}
df_land <- df_all_selected_mlt %>%
   group_by(`land_area`, `Population per sq. km.`, `Rural_Urban`) %>%
   filter(Rural_Urban == 'Rural' | Rural_Urban == "Urban") %>%
   summarise(sum = sum(`MLT`)) 

df_land %>%
   ggplot(aes(`land_area`, `Population per sq. km.`))+
   geom_jitter(aes(size=sum, color = Rural_Urban)) + 
   scale_x_log10() + 
   facet_wrap( ~ Rural_Urban)
```

```{r}
df_land_income <-df_all_selected_mlt %>%
   filter(`Sources of finance 1` == '01' |
             `Sources of finance 1` == '02'|
             `Sources of finance 1` == '03'|
             `Sources of finance 1` == '04'|
             `Sources of finance 1` == '05'|
             `Sources of finance 1` == '06'|
             `Sources of finance 1` == '07'|
             `Sources of finance 1` == '08'|
             `Sources of finance 1` == '09'|
             `Sources of finance 1` == '10'
             ) %>%
   group_by(`Land possessed`, `Sources of finance 1`, Rural_Urban) %>%
   filter(Rural_Urban == 'Rural' | Rural_Urban == "Urban") %>%
   summarise(sum_mlt = sum(`MLT`)) 
   
df_land_income %>%
   ggplot(aes(`Land possessed`, `Sources of finance 1`))+
   geom_tile(aes(fill = `sum_mlt`)) + 
   facet_wrap(~ Rural_Urban)

df_land_income
```
```{r}
df_land_income <-df_all_selected_mlt %>%
   filter(`Sources of finance 1` == '01' |
             `Sources of finance 1` == '02'|
             `Sources of finance 1` == '03'|
             `Sources of finance 1` == '04'|
             `Sources of finance 1` == '05'|
             `Sources of finance 1` == '06'|
             `Sources of finance 1` == '07'|
             `Sources of finance 1` == '08'|
             `Sources of finance 1` == '09'|
             `Sources of finance 1` == '10'
             ) %>%
   group_by(`Household Expenditure`, `Sources of finance 1`, Rural_Urban) %>%
   filter(Rural_Urban == 'Rural' | Rural_Urban == "Urban") %>%
   summarise(sum_mlt = sum(`MLT`)) 
   
df_land_income %>%
   ggplot(aes(`Household Expenditure`, `Sources of finance 1`))+
   geom_jitter(aes(size = `sum_mlt`, color = Rural_Urban)) + 
   facet_wrap(~ Rural_Urban)

df_land_income
```
```{r}
df_land_expend <-df_all_selected_mlt %>%
   group_by(`Household Expenditure`, `Land possessed`, Rural_Urban) %>%
   filter(Rural_Urban == 'Rural' | Rural_Urban == "Urban") %>%
   summarise(sum_mlt = sum(`MLT`)) 
   
df_land_expend %>%
   ggplot(aes(`Household Expenditure`, `Land possessed`))+
   geom_jitter(aes(size = `sum_mlt`, color = Rural_Urban)) +
   facet_wrap( ~ Rural_Urban)
```
