---
title: "Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```

```{r}
string <-"/Users/elliott/Downloads/Nss69/Nss69_1.2/Data/R6912L01.TXT"
read_tsv(file = string, col_names = FALSE)
```


- What are the columns in the data file? 

The first is a bunch of data codes strung together, then the last three might
be multipliers but we don't know what those are yet...

- what is a multiplier

 - what does USF mean?
 
 This is the the organization - IV unit is the smaller unit.
 
 - why does it say record length 143 when there are many more lines than that? 
 - All of the 'Levels' correlate to each other - do we need to match them based on the line or based on the codes? 
 - What is the 'MLT' text document?
 
 
 ## Questions from Elliot
 
 'results' are 
 - land  Schedule 1.2 item 13 block 3
 - spending spending amount (item 22, block 3)
 
 'indicators' are
 - population density
       - we found a separate dataset for population density of rural vs urban 
      areas for each district
      - The rural vs urban distinction appears on item 5 block 1 of the schedule
      - we will compile those two and assume that the definition of urban and rural
      is close enough
 - income source (item 10, block 3)
 
 - we want to filter to only look at certain population densities to 10k-16k people / km^2